\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[a4paper]{geometry}
\usepackage{fontawesome}
\geometry{ top=0.2in, left=0.2in, right=0.2in, bottom=0.2in}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{float}
\usepackage{tgbonum}
\usepackage{multicol}
\definecolor{shadecolor}{RGB}{200,200,200}

\begin{document}
\noindent \begin{center}
    \begin{huge}
        \textbf{Sarthak Rout}
    \end{huge}
    \\*
    \vspace{5pt}
     \href{https://www.linkedin.com/in/routsarthak/}{\textbf{\faLinkedin}/routsarthak}  | 
    \href{https://github.com/SarthakRout}{\textbf{\faGithub} /SarthakRout}  |
    \textbf{\href{https://www.facebook.com/sarthak.rout.1}{\faFacebook}} |
    \textbf{\href{https://sarthakrout.github.io}{\faGlobe}}
\end{center} 
\vspace{-3mm}
\noindent
Second Year Undergraduate \hfill \faEnvelope \ sarthakr@iitk.ac.in
\\
Department of CSE, IITK\hfill \faPhone \ +91-9664087578 
\noindent\colorbox{shadecolor}
{\parbox{\dimexpr\textwidth-2\fboxsep\relax}{\textsc{\textbf{Educational Background}}}}
\begin{table}[H]
    \vspace{-4mm}
    \resizebox{\textwidth}{!}{\begin{tabular}{l c c r}
    \textbf{Year} & \textbf{Degree/Exam} & \textbf{Institute} & \textbf{CPI/\%} \\ \midrule
    2019 - Present&B.Tech (Computer Science and Engineering)&Indian Institute of Technology, Kanpur& 9.5/10 \\ \midrule
    2019& CBSE(Class XII) & Sir Padampat Singhania Public School, Kota& 95.2/100 \\ \midrule
    2017& CBSE(Class X) & DAV Public School, Chandrasekharpur, BBSR & 10/10 \\ \bottomrule
    \end{tabular}}
    \vspace{-4mm}
\end{table}
\noindent\colorbox{shadecolor}
{\parbox{\dimexpr\textwidth-2\fboxsep\relax}{\textsc{\textbf{Scholastic Achievements}}}}
\begin{itemize}[topsep=8pt,itemsep=2pt, partopsep =2pt, parsep =2pt]
    \item Recipient of \textbf{Academic Excellence Award} from IIT Kanpur. \hfill \textit{2019}
    \item Secured All India Rank \textbf{202} in JEE (Advanced) among over 0.2 million students. \hfill \textit{2019}
    \item Secured 
    All India Rank \textbf{207} in JEE (Main) among over 1.3 million students. \hfill \textit{2019}
    \item Qualified for \textbf{OCSC of IJSO and IAO 2016, IOAA 2017, IOAA 2018, IChO and IOAA 2019} organised by HBCSE.
    \item Selected for \textbf{Kishore Vaigyanik Prostahan Yojana (SA)} fellowship with AIR \textbf{42}, IISc Bengaluru \hfill \textit{2018}
    \item Recipient of \textbf{National Talent Search} Scholarship, NCERT from MHRD, Gov. of India. \hfill \textit{2017}
\end{itemize}
\noindent\colorbox{shadecolor}
{\parbox{\dimexpr\textwidth-2\fboxsep\relax}{\textsc{\textbf{Projects}}}}

\renewcommand\labelitemii{$\circ$}

\begin{itemize}[topsep=8pt,itemsep=3pt, partopsep =2pt, parsep =3pt]
    \item \textbf{\href{https://github.com/SarthakRout/TestApp}{TestApp} - \href{http://baluate-74386.web.app/}{Live}}
    \hfill {(Autumn 2020)}
    \\*
    \textit{Self Project}
    \vspace{-2mm}
    \begin{itemize}
        \item Developed an assessment application using \textbf{Angular} integrated with \textbf{Firebase}.
        \item Implemented concepts of \textbf{routing}, \textbf{services}, \textbf{observables} and \textbf{modularity} and used \textbf{RxJs} library.
        \item Used it to conduct online MCQ examination  for about 20 students.
    \end{itemize}
    \vspace{-2mm}
    \item \textbf{Private Computation using Cryptographic Primitives} \hfill {(May  '20 - Jul '20)} \\* \textit{By SnT Club} | \textit{Mentor: Aditya Gulati }
    \vspace{-2mm}
    \begin{itemize}
        \item Learnt about \textbf{Private Computation, gRPC, Google Benchmark, Compiler Theory} and \textbf{Rust}.
        \item Learnt about \textbf{Function Secret Sharing, Fully Homomorphic Encryption} and \textbf{ Yao's Garbled Circuits}.
    \end{itemize}
    \vspace{-2mm}
    \item \textbf{InfoSec IITK} \hfill {(Feb '20 - Apr '20)} \\* \textit{By ACA} | \textit{Mentors: Priydarshi Singh, Varun Goyal}
    \vspace{-2mm}
    \begin{itemize}
        \item Learnt about \textbf{SQL Injection, XXS and XXE injection} along with how to prevent them.
        \item Learnt about \textbf{privilege escalation} using \textbf{Burp Suite, Metasploit, Nmap} etc. 
        \item Reported \textbf{critical} vulnerability in OARS, IITK which exposes databases storing grades of 6K+ students.
    \end{itemize}
    \vspace{-2mm}
    \item \href{https://github.com/SarthakRout/gradeLess} {\textbf {gradeLess - Course Project  ESC101}} \hfill { (Aug '19 - Nov '19)} \\* \textit{Under Dr. Piyush Rai, CSE} 
    \vspace{-2mm}
    \begin{itemize}
        \item Developed a \textbf{webapp} using \textbf{Angular} to check        True/False and MCQ questions of \textbf{printed} answer sheets.
        \item Integrated it with backend written in \textbf{Express} and used \textbf{Python} as scripting language for the Image Processing and Machine Learning part.
    \end{itemize}
    \vspace{-2mm}
\end{itemize}

\noindent\colorbox{shadecolor}
{\parbox{\dimexpr\textwidth-2\fboxsep\relax}{\textsc{\textbf{Technical Skills}}}}
\begin{multicols}{2}
    \begin{itemize}[topsep=5pt,itemsep=2pt, partopsep =2pt, parsep =2pt]
    \item \textbf{Programming Languages: } C, C++, Python, TypeScript, Octave/Matlab
    \item \textbf{Frameworks:} Angular, Express
    \item \textbf{Libraries :} Pandas, SciKit-Learn, OpenCV, Selenium
     \item \textbf{Tools :} Git, \LaTeX, Metasploit
\end{itemize}
\end{multicols}
\vspace{-3mm}
\noindent\colorbox{shadecolor}
{\parbox{\dimexpr\textwidth-2\fboxsep\relax}{\textsc{\textbf{Relevant Courses}}}}
\begin{table}[H]
    \vspace{-3mm}
    \begin{center}
    \vspace*{-1mm}
        \begin{tabular}{p{6cm} p{6cm} p{6cm} }
        Fundamentals of Computing* & Real Analysis and Calculus* & Linear Algebra and ODE \\*
        Data Structures and Algorithms & Numerical Analysis* & Number Theory\\* Introduction to Electronics  & Computer Organisation(o) & Software Development(o) \\* Modern Cryptology(o) & Quantum Computing(o) & \textit{ (* $\equiv$ A*, o $\equiv$ Ongoing)}
        \end{tabular}
    \vspace*{-7mm}
    \end{center}
\end{table}
% * : Awarded A* for exceptional performance

\noindent\colorbox{shadecolor}
{\parbox{\dimexpr\textwidth-2\fboxsep\relax}{\textsc{\textbf{Positions Of Responsibility and Extracurriculars}}}}
\vspace*{-7mm}
\begin{multicols}{2}
\begin{itemize}[topsep=5pt,itemsep=2pt, partopsep =2pt, parsep =2pt]
    \item Secretary, Programming Club
    % \begin{itemize}
    %     %\item Placed 2nd among UGs in Freshers' Programming Contest
    %     %\item Rated 5 $\star$ in %\href{https://www.codechef.com/users/sarthakrout}{Codechef}
    %     % \item Selected for Winter Camp , 2019
    %     % \item Ranked 3696 in Google Hash Code, 2020.
    %     % \item 
    %     % \item Wrote blogs on Medium and managed Sport Programmer of the Month Contest for the month of October
    % \end{itemize}
    \item Secretary, Entrepreneurship Cell (Startup Internship Program) 
    % \begin{itemize}
    %     % \item In E-Summit 2019, I worked in Hospitality Team, sold T-Shirts and helped in crowd control.
    %     % \item Contacted founders and CEOs of startups to participate in SIP Program
    % \end{itemize}
    \item Interned at Edvizo as Mentor in Maths teaching JEE Asiprants.
    \item Secured 16th position of Merit in HCL HackIITK Hackathon for detection of malware using Machine Learning. \textbf{\href{https://github.com/SarthakRout/HCL-HackIITK-Hackathon}{Link}}
    \item Competitive Programming: \textbf{\href{https://www.codechef.com/users/sarthakrout}{Codechef}}
    \item Bagged $2^{nd}$ position out of 250+ teams in Mathemania-2020, a competition based on math puzzles - \href{https://stamatics.github.io/mathemania/results}{\textbf{Results}}. 
\end{itemize}
\end{multicols}

\vspace*{\fill}
\noindent
 \textit{Hyperlinks are present at appropriate places in bold. } \hfill
 \textit{  Last Updated: \today }
\end{document}